plots with prolactin

### 2020-01-16 analysis/16_PRL.Rmd
new music figs

```{r music}

@@

>>>>

```{r music, fig.height=6, fig.width=6}

@@

p9 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  mytheme() +
  ylim(c(15,22)) +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21) +
  theme(axis.text  = element_blank(),
        axis.title = element_blank())

p9

p10 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(y = "Prolactin expression", x = "parental stage") +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p10

plot_grid(p10,p9, nrow = 2, align = "hv")
```
